Nesta attacks study

### 2021-08-11 paperDraft/paperDraft.Rmd
theoretical intro - on moderation expanded

>>>>

At the same time, only automated methods can scan through the massive amount of content being generated every day on different platforms. On Facebook, there are more than 3B comments and likes daily (https://martech.org/facebook-3-2-billion-likes-comments-every-day/), 500M tweets are sent daily on Twitter (https://www.oberlo.com/blog/twitter-statistics), and over 2B comments made by users of Reddit in 2020 (https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/) which is almost 3M comments made daily. With this amount of content, it's either impossible or extremely costly to scale the moderation workforce. One can also have doubts about the ethical aspects of hiring workers who are often unaware of how this kind of task will affect their well-being. Being submersed in the cyber-Augean stables takes a toll on many people. As examined by @roberts2014behind & @roberts2016commercial, workers who are hired for such tasks are often low-status and low-wage, isolated, and asked to keep what they've seen in secret under restrictive NDAs. Screening through the reported user-generated content is connected with exposure to violent and deeply disturbing materials, with child pornography, murders, or suicides as examples of the most extreme cases. This can lead to serious psychological damage, like depression, or PTSD (@roberts2014behind). Some of the employees filed a lawsuit against Facebook and as a result, the company agreed to pay $52M in compensation for mental health issues developed during the job (https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health).
Taking into consideration that Facebook employs 15K moderators (https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0) and most likely more are needed to keep up with the growing amount of content, with the parallel considerations about the negative effects of content moderation on mental health, a collaboration between humans and machines in this area seems inevitable. There is yet another aspect here - what moderators deal with is mostly content reported by humans. And as shown in various studies and reports, a lot of children, teens or even adults do not report cyberbullying or harassment online (LINKS: https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945 ; https://www.adl.org/free-to-play-2020 ; https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf).

# Pro-active and reactive moderation

#Collective Intelligence Approach

#Experimental Design

#Results

### 2021-08-11 paperDraft/paperDraft.tex
theoretical intro - on moderation expanded

@@

>>>>

At the same time, only automated methods can scan through the massive
amount of content being generated every day on different platforms. On
Facebook, there are more than 3B comments and likes daily
(\url{https://martech.org/facebook-3-2-billion-likes-comments-every-day/}),
500M tweets are sent daily on Twitter
(\url{https://www.oberlo.com/blog/twitter-statistics}), and over 2B
comments made by users of Reddit in 2020
(\url{https://old.reddit.com/r/blog/comments/k967mm/reddit_in_2020/})
which is almost 3M comments made daily. With this amount of content,
it's either impossible or extremely costly to scale the moderation
workforce. One can also have doubts about the ethical aspects of hiring
workers who are often unaware of how this kind of task will affect their
well-being. Being submersed in the cyber-Augean stables takes a toll on
many people. As examined by Roberts (2014) \& Roberts (2016), workers
who are hired for such tasks are often low-status and low-wage,
isolated, and asked to keep what they've seen in secret under
restrictive NDAs. Screening through the reported user-generated content
is connected with exposure to violent and deeply disturbing materials,
with child pornography, murders, or suicides as examples of the most
extreme cases. This can lead to serious psychological damage, like
depression, or PTSD (Roberts (2014)). Some of the employees filed a
lawsuit against Facebook and as a result, the company agreed to pay
\$52M in compensation for mental health issues developed during the job
(\url{https://www.theverge.com/2020/5/12/21255870/facebook-content-moderator-settlement-scola-ptsd-mental-health}).
Taking into consideration that Facebook employs 15K moderators
(\url{https://www.forbes.com/sites/johnkoetsier/2020/06/09/300000-facebook-content-moderation-mistakes-daily-report-says/?sh=6c6bdbbc54d0})
and most likely more are needed to keep up with the growing amount of
content, with the parallel considerations about the negative effects of
content moderation on mental health, a collaboration between humans and
machines in this area seems inevitable. There is yet another aspect here
- what moderators deal with is mostly content reported by humans. And as
shown in various studies and reports, a lot of children, teens or even
adults do not report cyberbullying or harassment online (LINKS:
\url{https://www.ctvnews.ca/canada/as-the-pandemic-forces-us-online-lgbtq2s-teens-deal-with-cyberbullying-1.5430945}
; \url{https://www.adl.org/free-to-play-2020} ;
\url{https://www.ditchthelabel.org/wp-content/uploads/2017/05/InGameAbuse.pdf}).

\hypertarget{pro-active-and-reactive-moderation}{%
\section{Pro-active and reactive
moderation}\label{pro-active-and-reactive-moderation}}

\#Collective Intelligence Approach

\#Experimental Design

\#Results

@@

\leavevmode\hypertarget{ref-roberts2014behind}{}%
Roberts, S. T. (2014). \emph{Behind the screen: The hidden digital labor
of commercial content moderation}. University of Illinois at
Urbana-Champaign.

\leavevmode\hypertarget{ref-roberts2016commercial}{}%
Roberts, S. T. (2016). \emph{Commercial content moderation: Digital
laborers' dirty work}.
